---
title: "week 7 coding workshop"
format: html
execute
  warning: false
  message: false
---

```{r}
library(tidyverse)
library(here)
library(lterdatasampler)

library(performance)
library(broom)
library(flextable)
library(ggeffects)
library(car)
library(naniar)
```

#linear models

How does stem length predict dry mass

```{r filtering data}
maples_data <- hbr_maples %>% 
  filter(year == 2003 & watershed == "Reference")
```

Visualize missing data

```{r missing data vis}
gg_miss_var(maples_data)
```

```{r data visualization}
ggplot(data = maples_data, aes(x = stem_length, y = stem_dry_mass)) + geom_point()

```

Model:

```{r linear-model-maples}
maples_model <- lm(stem_dry_mass ~ stem_length, data = maples_data)
maples_model
```

check assumptions

1.  linear relationship between variables: yes(used exploratory data visualization to do this

2.   independence of errors: yes! made on how data were collected

3.  homoskedasticity of errors: yes! making decision from residuals versus fitted plot/scale location plots

4.  normal distributed errors: yes! (looking at QQ plot of residuals

5.  <div>

    2.  <div>

        </div>

    </div>

```{r checking assumptions}
plot(maples_model)
par(mfrom = c(2, 2))
plot(maples_model)
```
